### 2018-10-07 Chapters/Chapter3.tex
Fixes

\begin{align*}
t_{ij}(t) = t_0e^{ie\bs{R}_{ij}\bs{A}(t)} = t_0e^{i\alpha_{ij} \cos(\omega t - \theta_{ij})} = t_0 \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} J_m(\alpha_{ij}) e^{im\omega t} = \sum t_{ij,m} e^{im\omega t}
\end{align*}

Where $t_{ij,m} = t_0 e^{i(\frac{\pi}{2}-\theta_{ij})m} J_m(\alpha_{ij})$ and $J_m(x)$ is the \textit{m}th Bessel function. Correspondingly $\hat{T}(t) = \sum_m \hat{T}_m e^{im \omega t}$.

@@

@@

\begin{align*}
i\hat{S}^{(1)}_d(t) &= -\sum_m \frac{\hat{T}_{d,m}}{Ud+m\omega}e^{im\omega t} \\
\hat{H}'^{(1)}(t) &= -\hat{T}_0(t)
\end{align*}

@@

\begin{equation}
\hat{H}'^{(2)}(t) = \left[i\hat{S}^{(2)}(t), U \hat{D} \right] - \left[ i\hat{S}^{(1)}(t), \hat{T}(t) \right] - d_t\hat{S}^{(2)}(t)
\end{equation}

Where the middle term is:

\begin{align*}
\left[ i\hat{S}^{(1)}(t), \hat{T}(t) \right] &= -\left[\sum_m \left( \frac{\hat{T}_{1m}}{U+m\omega} - \frac{\hat{T}_{-1m}}{U-m\omega} \right)e^{im \omega t}, \sum_n \left( \hat{T}_{-1n} +\hat{T}_{0n} + \hat{T}_{1n} \right) e^{in\omega t} \right] \\
&= -\sum_{mn} \left\{ \frac{\left[\hat{T}_{1m}, \hat{T}_{0n} \right]}{U+m\omega} + \frac{\left[\hat{T}_{1m}, \hat{T}_{-1n} \right]}{U+m\omega} - \frac{\left[\hat{T}_{-1m}, \hat{T}_{1n} \right]}{U-m\omega} - \frac{\left[\hat{T}_{-1m}, \hat{T}_{0n} \right]}{U-m\omega} \right\} e^{i(m+n)\omega t} \\
&= -\sum_{mn} \left\{ \frac{\left[\hat{T}_{1n}, \hat{T}_{0(m-n)} \right]}{U+n\omega} + \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{U+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{U-n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{0(m-n)} \right]}{U-n\omega} \right\} e^{im\omega t}
\end{align*}

@@

\begin{align*}
i\hat{S}^{(2)}_{dm} &= \sum_n \frac{\left[ \hat{T}_{dn}, \hat{T}_{0(m-n)} \right]}{(Ud+n\omega)(Ud+m\omega)} \\
\hat{H}'^{(2)}(t) &= \sum_{mn} \left( \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{U+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{U-n\omega} \right) e^{im\omega t}
\end{align*}

@@

\begin{equation}
\hat{H}_{eff}(t) = \hat{P}_0\hat{H}'^{(2)}(t)\hat{P}_0 = - \sum_{mn} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2}\hat{c}_{j \sigma_2}^\dagger \hat{c}_{i \sigma_2} \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_1} \left( \frac{t_{ji,(m-n)} t_{ij,n}}{U+n\omega} + \frac{t_{ji,n} t_{ij,(m-n)}}{U-n\omega} \right) e^{im\omega t}
\end{equation}

@@

\begin{align}
J_{ij}(t) &= \sum_{mn} 2\left( \frac{t_{ji,(m-n)} t_{ij,n}}{U+n\omega} + \frac{t_{ji,n} t_{ij,(m-n)}}{U-n\omega} \right) e^{im\omega t} \nonumber \\
&= \sum_{mn} 2\left( \frac{t_{ji,(m-n)} t_{ij,n} + t_{ji,-n} t_{ij,(m+n)}}{U+n\omega} \right) e^{im\omega t} \label{Jij1}
\end{align}

Now, $t_{ij,m} = t_0 e^{i(\frac{\pi}{2}-\theta_{ij})m} J_m(\alpha_{ij})$, using that $\theta_{ji} = \theta_{ij}$ and $\alpha_{ji} = -\alpha_{ij}$ and the properties $J_{-m}(x) = (-1)^mJ_m(x)$ and $J_m(-x) = (-1)^mJ_m(x)$ we can write \ref{Jij1} as:

\begin{equation}
J_{ij}(t) = \sum_{mn} 2t_0^2 e^{i(\frac{\pi}{2}-\theta_{ij})m}\left(\frac{J_{n-m}(\alpha_{ij})J_{n}(\alpha_{ij})+J_{n}(\alpha_{ij})J_{n+m}(\alpha_{ij})}{U+n\omega} \right) e^{im\omega t}
\end{equation}

@@

\begin{equation}
\label{Jij2}
J_{ij}(t) = \sum_{n} 4t_0^2 \frac{J_n(\alpha_{ij})^2}{U+n\omega}
\end{equation}

@@

\begin{equation}
J_{ij} = 4t_0^2 \left(\frac{\alpha_{ij}^2}{U+\omega} +\frac{1}{U} +\frac{\alpha_{ij}^2}{U-\omega} \right) = J_{ij}^0 + 4t_0^2 \alpha_{ij}^2 \left( \frac{1}{U+\omega} + \frac{1}{U-\omega} \right)
\end{equation}

@@

\begin{equation}
J_{ij}^{PP} = \begin{cases}
		J_{ij}^0 + 4t_0^2 \mathcal{E}^2 \left( \frac{1}{U+\omega} + \frac{1}{U-\omega} \right) & \text{for } \bs{R}_{ij} = \pm \hat{e}_x \\
J_{ij}^0 & \text{for } \bs{R}_{ij} = \pm \hat{e}_y
\end{cases} \quad 
\end{equation}

@@

\begin{equation}
J_{ij}^{CP} = J_{ij}^0 + 2t_0^2 \mathcal{E}^2 \left( \frac{1}{U+\omega} + \frac{1}{U-\omega} \right)
\end{equation}

>>>>

\begin{align*}
t_{ij}(t) = t_0e^{ie\bs{R}_{ij}\bs{A}(t)} = t_0e^{i\alpha_{ij} \cos(\omega t - \theta_{ij})} = t_0 \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t} = \sum t_{ij,m} e^{im\omega t}
\end{align*}

Where $t_{ij,m} = t_0 e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij})$ and $\mathcal{J}_m(x)$ is the \textit{m}th Bessel function \cite{Kitamura2017}. Correspondingly $\hat{T}(t) = \sum_m \hat{T}_m e^{im \omega t}$.

@@

\begin{equation}
\label{1stO}
\hat{H}'^{(1)}(t) = -\hat{T}(t) + \left[ i\hat{S}^{(1)}(t), U\hat{D} \right] - d_t\hat{S}^{(1)}(t)
\end{equation}

Now we expanding in $m,d$ and use $\left[ \hat{D}, \hat{S}^{(\nu)}_{dm} \right] = d\hat{S}^{(\nu)}_{dm}$ because $\hat{S}^{(\nu)}_{dm}$ changes the doublon number by $d$:

@@

\begin{align}
i\hat{S}^{(1)}_d(t) &= -\sum_m \frac{\hat{T}_{d,m}}{Ud+m\omega}e^{im\omega t} \label{1stOSpin}\\
\hat{H}'^{(1)}(t) &= -\hat{T}_0(t) \label{1stOH}
\end{align}

@@

\begin{equation}
\hat{H}'^{(2)}(t) = \left[i\hat{S}^{(2)}(t), U \hat{D} \right] - \left[ i\hat{S}^{(1)}(t), \hat{T}(t) \right] + \frac{1}{2}\left[ i\hat{S}^{(1)}(t), \left[ i\hat{S}^{(1)}(t), U\hat{D} \right] \right] - d_t\hat{S}^{(2)}(t)
\end{equation}

Using \ref{1stO} and using $\left[ i\hat{S}^{(1)}(t), d_t\hat{S}^{(1)}(t)\right] = 0$ due to different Fourier modes of the hopping operator being equal up to a constant, we can rewrite:

\begin{equation}
\hat{H}'^{(2)}(t) = \left[i\hat{S}^{(2)}(t), U \hat{D} \right] - \frac{1}{2}\left[ i\hat{S}^{(1)}(t), \hat{T}(t) - \hat{H}'^{(1)}(t)\right] - d_t\hat{S}^{(2)}(t)
\end{equation}

Using \ref{1stOSpin} and \ref{1stOH}, the middle term is:

\begin{align*}
&\left[ i\hat{S}^{(1)}(t), \hat{T}(t) - \hat{H}'^{(1)}(t)\right] = -\left[\sum_m \left( \frac{\hat{T}_{1m}}{U+m\omega} - \frac{\hat{T}_{-1m}}{U-m\omega} \right)e^{im \omega t}, \sum_n \left( \hat{T}_{-1n} + 2\hat{T}_{0n} + \hat{T}_{1n} \right) e^{in\omega t} \right] \\
&= -\sum_{mn} \left\{ \frac{2\left[\hat{T}_{1m}, \hat{T}_{0n} \right]}{U+m\omega} + \frac{\left[\hat{T}_{1m}, \hat{T}_{-1n} \right]}{U+m\omega} - \frac{\left[\hat{T}_{-1m}, \hat{T}_{1n} \right]}{U-m\omega} - \frac{2\left[\hat{T}_{-1m}, \hat{T}_{0n} \right]}{U-m\omega} \right\} e^{i(m+n)\omega t} \\
&= -\sum_{mn} \left\{ \frac{2\left[\hat{T}_{1n}, \hat{T}_{0(m-n)} \right]}{U+n\omega} + \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{U+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{U-n\omega} - \frac{2\left[\hat{T}_{-1n}, \hat{T}_{0(m-n)} \right]}{U-n\omega} \right\} e^{im\omega t}
\end{align*}

Altogether:

\begin{align*}
\hat{H}'^{(2)}(t) &= \sum_{mn} \left\{ \frac{\left[\hat{T}_{1n}, \hat{T}_{0(m-n)} \right]}{U+n\omega} + \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{2(U+n\omega)} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{2(U-n\omega)} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{0(m-n)} \right]}{U-n\omega} \right\} e^{im\omega t} \\
&-\sum_{d\neq 0}\sum_m (Ud+m\omega) i\hat{S}^{(2)}_{dm} e^{im\omega t}
\end{align*}

@@

\begin{align}
i\hat{S}^{(2)}_{dm} &= \sum_n \frac{\left[ \hat{T}_{dn}, \hat{T}_{0(m-n)} \right]}{(Ud+n\omega)(Ud+m\omega)} \label{2ndOSpin}\\
\hat{H}'^{(2)}(t) &= \frac{1}{2}\sum_{mn} \left( \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{U+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{U-n\omega} \right) e^{im\omega t} \label{2ndOH}
\end{align}

@@

\begin{equation}
\hat{H}_{eff}(t) = \hat{P}_0\hat{H}'^{(2)}(t)\hat{P}_0 = - \frac{1}{2}\sum_{mn} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2}\hat{c}_{j \sigma_2}^\dagger \hat{c}_{i \sigma_2} \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_1} \left( \frac{t_{ji,(m-n)} t_{ij,n}}{U+n\omega} + \frac{t_{ji,n} t_{ij,(m-n)}}{U-n\omega} \right) e^{im\omega t}
\end{equation}

@@

\begin{align}
J_{ij}(t) &= \sum_{mn} \left( \frac{t_{ji,(m-n)} t_{ij,n}}{U+n\omega} + \frac{t_{ji,n} t_{ij,(m-n)}}{U-n\omega} \right) e^{im\omega t} \nonumber \\
&= \sum_{mn} \left( \frac{t_{ji,(m-n)} t_{ij,n} + t_{ji,-n} t_{ij,(m+n)}}{U+n\omega} \right) e^{im\omega t} \label{Jij1}
\end{align}

Now, $t_{ij,m} = t_0 e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij})$, using that $\theta_{ji} = \theta_{ij}$ and $\alpha_{ji} = -\alpha_{ij}$ and the properties $\mathcal{J}_{-m}(x) = (-1)^m\mathcal{J}_m(x)$ and $\mathcal{J}_m(-x) = (-1)^m\mathcal{J}_m(x)$ we can write \ref{Jij1} as:

\begin{equation}
J_{ij}(t) = \sum_{mn} t_0^2 e^{i(\frac{\pi}{2}-\theta_{ij})m}\left(\frac{\mathcal{J}_{n-m}(\alpha_{ij})\mathcal{J}_{n}(\alpha_{ij})+\mathcal{J}_{n}(\alpha_{ij})\mathcal{J}_{n+m}(\alpha_{ij})}{U+n\omega} \right) e^{im\omega t}
\end{equation}

@@

\begin{equation}
\label{Jij2}
J_{ij}(t) = \sum_{n} 2t_0^2 \frac{\mathcal{J}_n(\alpha_{ij})^2}{U+n\omega}
\end{equation}

@@

\begin{equation}
J_{ij} = 2t_0^2 \left(\frac{\alpha_{ij}^2}{U+\omega} +\frac{1}{U} +\frac{\alpha_{ij}^2}{U-\omega} \right) = J_{ij}^0 + 2t_0^2 \alpha_{ij}^2 \left( \frac{1}{U+\omega} + \frac{1}{U-\omega} \right)
\end{equation}

@@

\begin{equation}
J_{ij}^{PP} = \begin{cases}
		J_{ij}^0 + 2t_0^2 \mathcal{E}^2 \left( \frac{1}{U+\omega} + \frac{1}{U-\omega} \right) & \text{for } \bs{R}_{ij} = \pm \hat{e}_x \\
J_{ij}^0 & \text{for } \bs{R}_{ij} = \pm \hat{e}_y
\end{cases} \quad 
\end{equation}

@@

\begin{equation}
J_{ij}^{CP} = J_{ij}^0 + t_0^2 \mathcal{E}^2 \left( \frac{1}{U+\omega} + \frac{1}{U-\omega} \right)
\end{equation}

\begin{section}{Hubbard model with SOI}

Now, let's investigate the effect of the electric field for the Hubbard model with SOI. As seen in \ref{AP3A} we can use the Peierls substitution to obtain the Hamiltonian:

\begin{equation}
\hat{H}(t) = -\sum_{\langle i,j \rangle, \sigma, \sigma'} e^{ie\bs{R}_{ij}\bs{A}(t)} (\delta_{\sigma \sigma'}t_0 + \bs{\Delta}_{ij}\bs{\sigma}_{\sigma \sigma'}) \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} = -\hat{T}(t) + \text{U}\hat{D}
\end{equation}

In this case the hopping operator $\hat{T}(t)$ includes the spin orbit interaction, but the time dependence is the same as before, we can use $e^{ie\bs{R}_{ij}\bs{A}(t)} =  \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t}$ where as before $e\bs{R}_{ij}\vec{A} = \alpha_{ij} e^{i \theta_{ij}}$ to write:

\begin{equation}
\hat{T}(t) = \sum_{\langle i,j \rangle, \sigma, \sigma'} \sum_m \Gamma_{ij,m}^{\sigma\sigma'} e^{im \omega t} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}
\end{equation}

Where we define $\Gamma_{ij,m}^{\sigma\sigma'} = e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij})(\delta_{\sigma, \sigma'}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma \sigma'})$ a scalar. Now we can follow the same procedure as in the previous section to obtain \ref{2ndOH}

\begin{equation}
\hat{H}'^{(2)}(t) = \frac{1}{2}\sum_{mn} \left( \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{\text{U}+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{\text{U}-n\omega} \right) e^{im\omega t}
\end{equation}

As before, we are only interested on how the Hamiltonian acts on the subspace of doublon number $d=0$. In that subspace we have:

\begin{equation}
\hat{H}_{eff}(t) = \hat{P}_0 \hat{H}'^{(2)}(t)\hat{P}_0 = - \frac{1}{2}\sum_{mn} \left( \frac{\hat{T}_{-1(m-n)}\hat{T}_{1n}  }{\text{U}+n\omega} + \frac{\hat{T}_{-1n}\hat{T}_{1(m-n)}}{\text{U}-n\omega} \right) e^{im\omega t}
\end{equation}

Where,

\begin{equation}
\hat{P}_0 \hat{T}_{-1a}\hat{T}_{1b} \hat{P}_0 = \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \Gamma_{ij,a}^{\sigma_1\sigma_2}\Gamma_{ji,b}^{\sigma_3\sigma_4} \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4}
\end{equation}

For any integers $a,b$. Therefore:

\begin{equation}
\hat{H}_{eff}(t) = -\frac{1}{2}\sum_{mn} \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} \left\{ \frac{\Gamma_{ij,(m-n)}^{\sigma_1\sigma_2}\Gamma_{ji,n}^{\sigma_3\sigma_4}}{\text{U}+n\omega} + \frac{\Gamma_{ij,n}^{\sigma_1\sigma_2}\Gamma_{ji,(m-n)}^{\sigma_3\sigma_4}}{\text{U}-n\omega} \right\} e^{im\omega t}
\end{equation}

We can rewrite:

\begin{align*}
\Gamma_{ij,(m-n)}^{\sigma_1\sigma_2}\Gamma_{ji,n}^{\sigma_3\sigma_4} &= e^{i(\frac{\pi}{2}-\theta_{ij})m}\mathcal{J}_{m-n}(\alpha_{ij})\mathcal{J}_n(\alpha_{ji})(\delta_{\sigma_1, \sigma_2}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\delta_{\sigma_3, \sigma_4}t_0+\bs{\Delta}_{ji}\bs{\sigma}_{\sigma_3 \sigma_4}) = \\
&= e^{i(\frac{\pi}{2}-\theta_{ij})m}\mathcal{J}_{m-n}(\alpha_{ij})\mathcal{J}_{-n}(\alpha_{ij})(\delta_{\sigma_1, \sigma_2}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\delta_{\sigma_3, \sigma_4}t_0-\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_3 \sigma_4}) = \\
&= e^{i(\frac{\pi}{2}-\theta_{ij})m}\mathcal{J}_{m-n}(\alpha_{ij})\mathcal{J}_{-n}(\alpha_{ij}) \left[ \delta_{\sigma_1, \sigma_2}\delta_{\sigma_3, \sigma_4}t_0^2+t_0\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) + \mathcal{O}(\bs{\Delta}_{ij}^2) \right]
\end{align*}

Where we used $\theta_{ji} = \theta_{ij}$, $\alpha_{ji} = - \alpha_{ij}$ and $\bs{\Delta}_{ji} = -\bs{\Delta}_{ij}$. We neglect the $\mathcal{O}(\bs{\Delta}_{ij}^2)$ term. The term proportional to $t_0^2$ will lead to the modified exchange interaction, and it is exactly the same as in the previous section. The term proportional to $t_0\bs{\Delta}_{ij}$ will lead to the modified DMI interaction. Define:

\begin{equation}
\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \sum_{mn}e^{i(\frac{\pi}{2}-\theta_{ij})m} \left\{ 
    \frac{\mathcal{J}_{m-n}(\alpha_{ij})\mathcal{J}_{-n}(\alpha_{ij})}{\text{U}+n\omega} +
    \frac{\mathcal{J}_n(\alpha_{ij})\mathcal{J}_{n-m}(\alpha_{ij})}{\text{U}-n\omega}    
    \right\}e^{im\omega t}
\end{equation}

Now, introducing the spin operators \ref{SpinOperators}, using relations \ref{SpinOperatorInv1} and \ref{SpinOperatorInv2} and taking into account that in this subspace $n_{i\uparrow}+n_{i\downarrow}=1$ we obtain:

\begin{align*}
\hat{H}_{eff}(t) &\approx -\frac{1}{2}\sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
&\times \left[ \delta_{\sigma_1, \sigma_2}\delta_{\sigma_3, \sigma_4}t_0^2+t_0\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) \right]\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \\
&= -\frac{t_0^2}{2} \sum_{\langle i,j \rangle \sigma, \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \bs{S}_i\bs{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\bs{S}_j\bs{\sigma}_{\sigma \sigma'}\right)\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) - \\
&- \frac{t_0}{2} \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
&\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4})\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \\
&= \sum_{\langle i,j \rangle} \left( t_0^2 \bs{S}_i\bs{S}_j + 2it_0\bs{\Delta}_{ij} \bs{S}_i \times \bs{S}_j \right) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) =\\
&= \sum_{\langle i,j \rangle} J_{ij}(t)\bs{S}_i\bs{S}_j +\bs{D}_{ij}(t)\bs{S}_i \times \bs{S}_j = \\
&= \hat{H}_J'(t)+\hat{H}_D'(t)
\end{align*}

Where we also used relations \ref{SpinRel1} and \ref{SpinRel2}. We have:

\begin{align}
J_{ij}(t) &= t_0^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
\bs{D}_{ij}(t) &= 2it_0\bs{\Delta}_{ij} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
\end{align}

For $\bs{D}_{ij}(t)$ this is:

\begin{equation}
\bs{D}_{ij} = 2it_0 \bs{\Delta}_{ij} \sum_{mn}e^{i(\frac{\pi}{2}-\theta_{ij})m} \left\{ 
    \frac{\mathcal{J}_{m-n}(\alpha_{ij})\mathcal{J}_{-n}(\alpha_{ij})}{\text{U}+n\omega} +
    \frac{\mathcal{J}_n(\alpha_{ij})\mathcal{J}_{n-m}(\alpha_{ij})}{\text{U}-n\omega}    
    \right\}e^{im\omega t}
\end{equation}
